Wolbachia, Toxoplasma and O. Cordyceps: Extreme Host-Manipulating Microbes That Changed the World

### 2015-12-16 paper.tex
Added image

@@

@@

>>>>

\begin{figure}[!ht]
    \centering
    \includegraphics[width=.4\textwidth]{images/Wolbachia.png}
    \caption{\textit{Wolbachia} bacteria (Green circles) inside a host cell. It is difficult to tell that there is a bacteria present if one is unaware.\cite{Wwiki_image} }
    \label{fig:wolbachiha_tree}
\end{figure}

@@

\textit{Ophiocordyceps unilateralis} was first discovered by the British naturalist Alfred Russel Wallace who, probably not coincidently, is best known for independently conceiving the theory of evolution through natural selection.

@@

\section*{Added To The Class?}
